### 2012-09-04 sections/conclusion.tex
* back to 8 pages   * reduced all figure sizes to 0.9/linewidth   * removed tcpdump, wireshark, libpcap paragraph with citations
revision with professor's comments   * conclusion, with blurb on usefulness of benchmarking queries   * removed ungrouper graph

We presented \ac{NFQL}, an efficient C implementation of the stream-based flow
query language. The language allows applying absolute (or relative) filters,
aggregating flows into groups, evaluating intricate timing relationships among
them, and merging them into one collection. \ac{NFQL} can execute such complex
query tasks in matter of minutes, thereby expanding the scope of current flow
record processing tools. The conducted performance evaluations reveal that
\ac{NFQL} is on par with tools that support only absolute filters. SiLK, the
only openly available package that provides tools that are similar to the rest
of \ac{NFQL}'s processing pipeline appears faster. This is because it can
optimize its operations in favor of the limited set of comparisons that are
only based on equality, and its usage of a different file storage format.
\todo{...}

>>>>

We presented \ac{NFQL}, an efficient C implementation of the stream-based flow
query language. The language allows applying absolute (or relative) filters,
aggregating flows into groups, evaluating timing relationships among them, and
merging them into one collection. \ac{NFQL} can execute such complex queries
in matter of minutes, thereby expanding the scope of current flow record
processing tools. The conducted performance evaluations reveal that \ac{NFQL}
is on par with tools that support only absolute filters. SiLK, the only openly
available package that provides tools that are similar to the rest of
\ac{NFQL}'s processing pipeline appears faster. This is because it can
optimize its operations in favor of the limited set of comparisons that are
only based on equality, and its usage of a different file storage format. The
evaluation queries developed as a part of this research work may also develop
into a more general benchmark suite for flow query tools and platforms.

### 2012-09-04 sections/evaluation.tex
revision with professor's comments   * conclusion, with blurb on usefulness of benchmarking queries   * removed ungrouper graph

The last set of queries attempt to stress the ungrouper stage. They reuse the
entire merger queries as is, but enable the ungrouper as well. This means,
that the ungrouper now attempts to unfold the merged groups returned by the
merger to write their member flow records to \texttt{flowtools} files.
However, since the merger receives each flow record as its own filtered group,
each merged group has only one member. As a result, the ungrouper ends up
rewriting the merged groups as \texttt{flowtools} files using the same
\texttt{zlib} compression level. The ratio of the number of result flow
records to twice the number of the flow records in the input trace is plotted
against time. The evaluation results are shown in Fig.
\ref{fig:benchmarks-ungrouper}.

\begin{figure}[h!]
  \begin{center}
    \includegraphics* [width=0.9\linewidth]{ungrouper}
    \caption{Ungrouper Stage}
    \label{fig:benchmarks-ungrouper}
  \end{center}
\end{figure}

It can be seen that the behavior of the ungrouper is similar to that shown by
the merger. Since, the ungrouper also has to write the entire merged groupset
to files, as is previously done by merger, the execution engine takes twice the
amount of time. It is important to note, that SiLK does not have such an
equivalent ungrouping tool and is therefore not considered in this final
evaluation.

>>>>

The last set of queries attempt to stress the ungrouper stage. They reuse the
entire merger queries as is, but enable the ungrouper as well. This means,
that the ungrouper now attempts to unfold the merged groups returned by the
merger to write their member flow records to \texttt{flowtools} files.
However, since the merger receives each flow record as its own filtered group,
each merged group has only one member. As a result, the ungrouper ends up
rewriting the merged groups as \texttt{flowtools} files using the same
\texttt{zlib} compression level. This means that the execution engine end up
taking twice the amount of time than the merger. It is important to note, that
SiLK does not have such an equivalent ungrouping tool and is therefore not
considered in this final evaluation.
